Hydra Battles and Cie

### 2021-06-01 doc/part-hydras.tex
correction of typos

Thus, for instance, $L_{\omega^3}(3)=L_{\omega^2\times 4}(3)$.
Thus, we obtain an exact expression of this number.

@@

This number is quite big. Using \texttt{Ocaml}'s \texttt{float} arithmetic,
we can [under-]approximate it by $2^{3.8\times10^{30}}\times 3.8\times{10^{30}}$.

@@

In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

\begin{remark}
  Indeed, the functions presented in this section are a \emph{variant} of the Hardy hierarchy of functions. In the future versions of this development, we will correct the references to the litterature. For the time being, we call our functions $H'\_alpha$ in order to underline the difference from ``classic'' Hardy functions.
\end{remark}

@@

@@

>>>>

Thus, for instance, $L_{\omega^3}(3)=L_{\omega^2\times 4}(3)$.

@@

This number is quite big. Using \texttt{Ocaml}'s \texttt{float} arithmetic,
we can under-approximate it by $2^{3.8\times10^{30}}\times 3.8\times{10^{30}}$.

@@

In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the  \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

\begin{remark}
  Indeed, the functions presented in this section are a \emph{variant} of the Hardy hierarchy of functions. In the future versions of this development, we will correct the references to the litterature. For the time being, we call our functions $H'_\alpha$ in order to underline the difference from ``classic'' Hardy functions.
\end{remark}

@@

By elimination, we get a catalogue of properties of the functions $L'_\alpha$:

\begin{Coqsrc}
Section Abstract_Properties.
 Variable alpha : E0.

 Theorem H'_alpha_mono : strict_mono (H'_ alpha).

 Theorem H'_alpha_gt : alpha <> Zero ->
        forall n, n < H'_ alpha n.

 Theorem H'_alpha_Succ_le :
        H'_ alpha <<= H'_ (Succ alpha).

 Theorem H'_alpha_dom :
    dominates_from 1 (H'_ (Succ alpha)) (H'_ alpha).

 Theorem H'_restricted_mono_l :
    forall beta n, Canon_plus n alpha beta -> 
                                 H'_ beta n <= H'_ alpha n.

  Lemma H'_alpha_ge_id : id <<= H'_ alpha.

  Lemma H'_alpha_mono_weak : forall k l, k <= l ->
                                        H'_ alpha k <= H'_ alpha l.

End Abstract_Properties.
\end{Coqsrc}

Using a few lemmas \emph{à la} Ketonen-Solovay, we prove that
if $\alpha<\beta$, then $H'_\beta$ eventually dominates
$H'_\alpha$.
We let the reader look at its proof (Section \texttt{Proof\_of\_H'\_mono\_l} of \href{../theories/html/hydras.Epsilon0.Hprime.html\#H_}{Epsilon0.Hprime}).

\noindent
\begin{Coqsrc}
  H'_dom : forall alpha beta : E0, alpha o< beta ->
  dominates_strong (H'_ beta) (H'_ alpha).
\end{Coqsrc}

@@

%------------------------------------------------------
\section{A certified catalogue of rapidly growing functions}

In this section, we try to present an abstract of the properties of the main variants of fast-growing hierarchies of functions
we fauund in the litterature or we had to define as helpers in our proofs.

\subsection{Ketonen-Solovay's \texttt{F\_alpha}}

  This hierarchy is presented p.280 of~\cite{KS81} as `` a trivial variant of one introduced by Wainer ''.
  Let us recall the equations shown in Sect.~\vref{F_equations}.

\begin{itemize}
\item $F_0(i)=i+1$
\item $F_{\beta+1}(i)= (F_\beta)^{(i+1)}(i)$, where $f^{(i)}$ is the $i$-th iterate of $f$.
\item $F_\alpha(i) = F_{\canonseq{\alpha}{i}} (i)$ if $\alpha$ is a limit ordinal.
\end{itemize}

Note that \cite{KS81} defines also $F_{\epsilon_0}$ (by the third equation). Since $\epsilon_0$ is not representable in type \texttt{E0}, our translation in \coq{} does not take $F_{\epsilon_0}$ into account.

Several properties of $F_\alpha$ are already presented in Sect.~\ref{F_equations}.
